\begin{document}

  Problems where sympy doesn't compare satisfactorily to Mathematica (e.g. where I want to add capability):

Mathematica:

In[3]:= Integrate[Log[eh/e]*Sqrt[e - ec*Vp], e]

Out[3]= 2/9 (6 ec^(3/2) Vp^(3/2)
     ArcTan[Sqrt[e - ec Vp]/(Sqrt[ec] Sqrt[Vp])] +
   Sqrt[e - ec Vp] (2 (e - 4 ec Vp) + 3 (e - ec Vp) Log[eh/e]))

Sympy:

In [17]: integrate(log(eh/e) * sqrt(e - ec * Vp),e)
Out[17]: Integral(sqrt(-Vp*ec + e)*log(eh/e), e)

def null_safe(rule):
    """ Return original expr if rule returns None """
    def null_safe_rl(expr):
        result = rule(expr)
        if result is None:
            return expr
        else:
            return result
    return null_safe_rl

def do_one(*rules):
    """ Try each of the rules until one works. Then stop. """
    def do_one_rl(expr):
        for rl in rules:
            result = rl(expr)
            if result != expr:
                return result
        return expr
    return do_one_rl

def switch(key, ruledict):
    """ Select a rule based on the result of key called on the function """
    def switch_rl(expr):
        rl = ruledict.get(key(expr), identity)
        return rl(expr)
    return switch_rl

def key(integral):
    integrand = integral.integrand

    if isinstance(integrand, TrigonometricFunction):
        return TrigonometricFunction
    elif isinstance(integrand, sympy.Derivative):
        return sympy.Derivative
    elif symbol not in integrand.free_symbols:
        return sympy.Number
    else:
        for cls in (sympy.Pow, sympy.Symbol, sympy.exp, sympy.log,
                    sympy.Add, sympy.Mul, sympy.atan, sympy.asin, sympy.acos, sympy.Heaviside):
            if isinstance(integrand, cls):
                return cls


Nested functions can easily be used to return a function. And that can be used to create the nice double paranthese syntax that I've seen and had yet to understand:

import math
def make_cylinder_volume_func(r):
    def volume(h):
        return math.pi * r * r * h
    return volume

volume = make_cylinder_volume_func(5)(3)
print(volume)

Ok this is making some sense: do_one is a function with a nested function that it returns. Thus to perform an assignment using do_one, we need to pass two parentheses of arguments. The first parenthetical group is the rules we want to consider, and the second paranthetical group is the expression.

Example integrands where my new rule works:

\begin{enumerate}
\item ln(x) * sqrt(x)
\item ln(x) * x**7
\item ln(x-7) * x**7
\item ln(x**2) * x**7
\end{enumerate}

Integrands where new rule fails:

\begin{enumerate}
\item sqrt(x-y) * ln(x)
  \begin{itemize}
  \item Output: (x - y)**(3/2) * (2 * log(x) / 3 - 4/9)
  \item Expected output: 2/9 * (-6 * y**(3/2) * atan(sqrt(x - y) / sqrt(y)) + sqrt(x - y) * (-2x + 8y + 3(x-y)*log(x)))
  \end{itemize}
\item (x-y)**3 * log(x)
  \begin{itemize}
  \item Output: (x - y)**4*(log(x)/4 - 1/16)
  \item expected output: 1/48 x (-3 x^3 + 16 x^2 y - 36 x y^2 + 48 y^3 + 12 (x^3 - 4 x^2 y + 6 x y^2 - 4 y^3) Log[x])
  \end{itemize}
\end{enumerate}

Currently, where log_pow_product rule shines (or is even used) is when dealing with logarithms multiplied by monomials with non-integer exponents. Currently it only works when the logarithm is simply the logarithm of the argument, and when the monomial base is a simple sympy.Symbol.

I am going to limit myself to considering a log function multiplied by a power function. The arguments of both the log function and the power function can be Mul or Add.

Boom, baby! I got my issue request integral to work under certain conditions for y. Boom baby!!! That requires the s_over_x rule.

So the line in manualintegrate.py that's causing the manual tests to fail is this line:

        polys = [arg for arg in integrand.args if (arg.is_polynomial(symbol) or isinstance(arg, sympy.Pow))]

where the old line was:

polys = [arg for arg in integrand.args if (arg.is_polynomial(symbol))]

New Integrand capabilities with my PR:

sqrt(x-y) * log(z/x) [neither integrate or manualintegrate could handle this]
sqrt(x) * log(x) [manualintegrate could not handle this but integrate could]
sqrt(a*x + b) / x [manualintegrate could not handle this but integrate could]

Unsupported integrands (even with my PR):

u**2 / (u**2 - b) [manualintegrate cannot handle this but integrate can]

Good to know that the polylog solution comes from the meijerg integration method.

The 107 tests in test_integrals on 10847 branch take 69.12 seconds to solve.
The 19 tests in test_manual on 10847 branch take 29.12 seconds to solve. (longest test is my test, particularly the big rational function problem)

The 17 tests in test_manual on master branch take 8.65 seconds to solve.
The 107 tests in test_integrals on master branch take 69.16 seconds.

So just based off those speed numbers, I see no reason why my test_integrals should display.

I'm curious how in one case there are 107 tests in test_integrals, but in Travis's ``slow'' test, there only appear to be 3 tests in test_integrals. That's something to explore after lunch.

(1 + 2*exp(-2*I*pi*i*x/L) + exp(-4*I*pi*i*x/L))/(4*a*exp(-2*I*pi*i*x/L) + 4*b*x*exp(-2*I*pi*i*x/L))

2*Piecewise((x/(4*a), Eq(b, 0)), (log(4*a + 4*b*x)/(4*b), True)) + Integral(1/(4*a*exp(-2*I*pi*i*x/L) + 4*b*x*exp(-2*I*pi*i*x/L)), x) + Integral(1/(4*a*exp(2*I*pi*i*x/L) + 4*b*x*exp(2*I*pi*i*x/L)), x)

1/(4*a*exp(2*I*pi*i*x/L) + 4*b*x*exp(2*I*pi*i*x/L))

Integral(1/(4*a*exp(2*I*pi*i*x/L) + 4*b*x*exp(2*I*pi*i*x/L)), x)

By itself with 10847:

test_issue_7130 - Took 19.387 seconds
Still running at 51.653 seconds
test_issue_7130 - Took 14.441 seconds
test_issue_7130 - Took 14.324 seconds
Still running at 108.912 seconds (using two processors at 100%)
test_issue_7130 - Took 16.119 seconds
Still running at 62 seconds
test_issue_7130 - Took 12.612 seconds

By itself with master:

test_issue_7130 - Took 13.190 seconds
test_issue_7130 - Took 13.245 seconds
test_issue_7130 - Took 12.713 seconds
test_issue_7130 - Took 13.869 seconds
test_issue_7130 - Took 16.770 seconds

Back to 10847:
Still running at 36.246 seconds
test_issue_7130 - Took 13.795 seconds

To 0d09436
test_issue_7130 - Took 12.526 seconds
test_issue_7130 - Took 16.150 seconds
test_issue_7130 - Took 13.179 seconds
test_issue_7130 - Took 13.391 seconds
test_issue_7130 - Took 13.771 seconds

/home/lindsayad/miniconda2/envs/python3SympyDev/lib/python3.5/subprocess.py

To 10847 in debug mode:
test_issue_7130 - Took 62.913 seconds
test_issue_7130 - Took 65.362 seconds
test_issue_7130 - Took 58.745 seconds

/home/lindsayad/miniconda2/envs/python3SympyDev/lib/python3.5/site-packages/sympy/core/numbers.py

-Integral(2*exp(2*I*pi*i*x/L)/(a*exp(2*I*pi*i*x/L) + b*x*exp(2*I*pi*i*x/L)), (x, 0))/4 + Integral(2*exp(2*I*pi*i*x/L)/(a*exp(2*I*pi*i*x/L) + b*x*exp(2*I*pi*i*x/L)), (x, L))/4 - Integral(exp(4*I*pi*i*x/L)/(a*exp(2*I*pi*i*x/L) + b*x*exp(2*I*pi*i*x/L)), (x, 0))/4 + Integral(exp(4*I*pi*i*x/L)/(a*exp(2*I*pi*i*x/L) + b*x*exp(2*I*pi*i*x/L)), (x, L))/4 - Integral(1/(a*exp(2*I*pi*i*x/L) + b*x*exp(2*I*pi*i*x/L)), (x, 0))/4 + Integral(1/(a*exp(2*I*pi*i*x/L) + b*x*exp(2*I*pi*i*x/L)), (x, L))/4

pass

This is the integral passed to manualintegrate for the stupid slow integral test:
(1 + 2*exp(-2*I*pi*i*x/L) + exp(-4*I*pi*i*x/L))/(4*a*exp(-2*I*pi*i*x/L) + 4*b*x*exp(-2*I*pi*i*x/L))

result from sage:

-1/4*e^(2*pi*a/(L*b))*exp_integral_e(1, 2*pi*(b*x + a)/(L*b))/b - 1/4*e^(-2*pi*a/(L*b))*exp_integral_e(1, -2*pi*(b*x + a)/(L*b))/b + 1/2*log(b*x + a)/b

Result of actual test integral with master branch:

-Integral(2*exp(2*I*pi*i*x/L)/(a*exp(2*I*pi*i*x/L) + b*x*exp(2*I*pi*i*x/L)), (x, 0))/4 + Integral(2*exp(2*I*pi*i*x/L)/(a*exp(2*I*pi*i*x/L) + b*x*exp(2*I*pi*i*x/L)), (x, L))/4 - Integral(exp(4*I*pi*i*x/L)/(a*exp(2*I*pi*i*x/L) + b*x*exp(2*I*pi*i*x/L)), (x, 0))/4 + Integral(exp(4*I*pi*i*x/L)/(a*exp(2*I*pi*i*x/L) + b*x*exp(2*I*pi*i*x/L)), (x, L))/4 - Integral(1/(a*exp(2*I*pi*i*x/L) + b*x*exp(2*I*pi*i*x/L)), (x, 0))/4 + Integral(1/(a*exp(2*I*pi*i*x/L) + b*x*exp(2*I*pi*i*x/L)), (x, L))/4

In other words zero integration is done. So again I am getting penalized because I made manualintegrate do more work!!!

Pass
Pass
Pass
Pass
Pass


\end{document}
